Exploring probability distributions for bivariate temporal granularities

### 2019-11-20 main.Rmd
circular granularity definition update

Suppose,
z denotes the index of the tsibble. Also represents the bottom granularity.
Let G be a periodic linear granularity, not equal to the bottom granularity, with k(BG,G) as the period length of the bottom granularity with respect to linear granularity G.
C(BG, G) is the circular granularitiy relating linear granularity G to the bottom granularity. Then,  C(BG, G) is given as follows: 
Then, $$C_{BG, G}(z) = G(z\mod k(BG,G))$$

>>>>

Suppose,
z denotes the index set.
BG denotes the index of the tsibble. Also represents the bottom granularity.
Let G be a linear granularity, periodic with respect to BG.
k(BG,G) be the period length of the bottom granularity with respect to linear granularity G.
C(BG, G) is the circular granularitiy relating linear granularity G to the bottom granularity. Then,  C(BG, G) is given as follows: 
Then, $$C_{BG, G}(z) = G(z\mod k(BG,G))$$.

For example, suppose the bottom granularity day and circular granularity day-of-week are represented by D and $$C_{day, week}$$ respectively, then we will have:

$$C_{day, week}(z) = D(z\mod 7)$$.

Since, the period length of days with respect to weeks is 7.

All circular granularities can be expressed in terms of the bottom linear granularity with equation.
